What Makes Deep Network Representations Good for Visual Recognition?

### 2015-04-07 paper_for_review.tex
v1.3

Although deep neural networks have been successfully pushing the boundaries of computer vision by breaking the records of ImageNet Challenges (ILSVRC) \cite{russakovsky} year after year \cite{krizhevsky2012imagenet, sermanet2013overfeat, szegedy2014going}, our understanding of the properties of these networks arguably remains limited, since we cannot yet fully answer the question ``what makes a deep network good?'' In this paper, we investigate two important facets of this question: (1) why deep networks are better than shallow networks, and (2) among networks of the same depth, why certain networks are better than others (Fig.~\ref{fig:perf}). Specifically, from the point of view that successful networks are forming ``better'' representations of visual inputs that are more separable to the final-stage linear classifiers, we want to identify the crucial properties that are required for forming (or learning) better representations.

>>>>

Although deep neural networks have been successfully pushing the boundaries of computer vision by breaking the records of ImageNet Challenges (ILSVRC) \cite{russakovsky2014imagenet} year after year \cite{krizhevsky2012imagenet, sermanet2013overfeat, szegedy2014going}, our understanding of the properties of these networks arguably remains limited, since we cannot yet fully answer the question ``what makes a deep network good?'' In this paper, we investigate two important facets of this question: (1) why deep networks are better than shallow networks, and (2) among networks of the same depth, why certain networks are better than others (Fig.~\ref{fig:perf}). Specifically, from the point of view that successful networks are forming ``better'' representations of visual inputs that are more separable to the final-stage linear classifiers, we want to identify the crucial properties that are required for forming (or learning) better representations.
